\documentclass[main.tex]{subfiles}
\begin{document}

\subsection{Appendix A -  Timeline\/Milestones}
\label{sec: A}
\begin{enumerate}
    
\item 10/10/2016 - Announcement

\item 10/12/2016 - 3 ideas:   a list of 3 ideas and brief description of each and why you are interested in each of them)

\item 10/17/2016: SP Status 1- Definitions of 2 of 4 exercises, identifying resources, lab instruction (outline, network configuration) draft, Lab report draft (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class).

\item 10/24/2016: SP Status 2 -Definitions of 4 of 4 exercises, identifying resources,  Lab instruction (Ex 1) draft,  Lab report draft (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class).

\item \textbf 10/31/2016: SP Status 3 - Demo of Exercise 1, ShareLatex Lab Instruction (Ex 1, 2) draft, ShareLatex Lab Report (Ex 1) draft (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class).

\item 11/9/2016:SP Status 4 - Demo of Exercises 1, 2, ShareLatex Lab Instructions (Ex 1, 2, 3) draft \#1, ShareLatex Lab Report (Ex 1, 2) draft (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class). 

\item 11/16/2016:{\large \textbf SP Status 5 -Demo of Exercises 1, 2, 3, ShareLatex Lab Instructions (Ex 1, 2, 3, 4) draft \#1,ShareLatex Lab Report (Ex 1, 2, 3) draft (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class).}
\item 11/30/2016: Dry Run 1 -Demo of Exercise 1, 2, 3, 4, ShareLatex Lab Instruction (Ex 1, 2, 3, 4) draft\#2, ShareLatex Lab Report (Exercise 1, 2, 3, 4) draft (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class).

\item 12/7/2016: Dry Run 2 - Demo of Exercise 1, 2, 3, 4,ShareLatex Lab Instruction (Ex 1, 2, 3, 4) close to final,ShareLatex Lab Report (Exercise 1, 2, 3, 4) close to final (As an appendix, provide status including what you have done, action items, that is, To Do List and by Whom (owner) to be completed before next class).

\item 12/14/2016 (1:00 am - 3:00 pm) : Final Demo -  (Live or Video/Videos) for scenarios based of the exercises during the finals,ShareLatex Final Lab Instructions,ShareLatex Final Lab Report, Final Double-Sided OnePager (including draft of final demo), Final 5-Slide Presentation (include scenarios of final demo).
\end{enumerate}

\newpage

\subsection{Appendix B - Weekly Status Updates}
\label{sec:B}
\begin{enumerate}[leftmargin=12mm,labelsep=0.1cm]
    \item[] \textbf{\Large \underline{Status \#3 TO Do List - 10/31/2016}}
    \begin{enumerate}
        \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
        \begin{enumerate}
            \item TACACS+ Server is successfully set up on Windows 7 vm, done by BOTH. 
            \item Demo will involve showing the instructions, some of the report, and the majority of the 1st exercise. This includes the editing of the authentication xml file, showing proof of the service, etc.
        \end{enumerate}
        \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
        \begin{enumerate}
            \item Find a way to allow remote login from another vm.
            \item Think about using GNS3 to emulate a cisco router
            \item Get the lab report up to date with the lab instructions.
            \item (TROY) Finish Exercise 1. Add step (or exercise) for comparison of RADIUS and TACACS+. Integrate wireshark. 
            \item (ISAAC) Finish Exercise 2. Work on exploiting the vulnerabilities associated with the tacacs+ server.
            \item Begin Exercise 3. This will have all of the extra features that TACACS+ has, such as OTP, and verification/troubleshooting.
            \item Begin Exercise 4. This will have a comparison between running an tacacs+ server on windows and linux.
            \item INSTALL LO INTERFACE ON WINDOWS 7 to be able to capture packets.
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
\hfill \break
\begin{enumerate}[leftmargin=12mm,labelsep=0.1cm]
    \item[] \textbf{\Large \underline{Status \#4 To DO List - 11/9/2016}}
    \begin{enumerate}
        \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
        \begin{enumerate}
            \item Show instructions of the 4th exercise, and add it to template on the lab report.
            \item Still cannot find out how to integrate wireshark to capture tacacs+ packets.
            \item how to emulate cisco router and connect to it
            \item Finished up setting up tacacs on ubuntu. Write this up
            \item find out how to work gns3 (Am having a hard time with it)
            \item fix lo interface on windows
        \end{enumerate}
        \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
        \begin{enumerate}
            \item Assess vulnerability. Finish Exercises 1 and 4? (Instructions and Lab report)
            \item make video demo for next status
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
\hfill \break
\begin{enumerate}[leftmargin=12mm,labelsep=0.1cm]
    \item[] \textbf{\Large \underline{Status \#5 To DO List - 11/9/2016}}
    \begin{enumerate}
        \item \textbf{Pre-class - Status of Last Week's Action Items and/or Milestone due this week}
        \begin{enumerate}
            \item (Troy) - Show video demo that is put on youtube. Work on screenshots of the exercise shown in the video. 
            \item (BOTH) Finalize exercise 1 and 2 (almost done) by adding questions where noted.
            \item (BOTH) Explain the different types of vulnerabilities that we found (MitM w/ arp spoofing & DOS overflow)
            \item (Isaac) Learned Scapy to initiate vulnerability
            \item (Troy) Learned GNS3 / cisco router configuration
        \end{enumerate}
        \item \textbf{Post-class - Action Items for Next week and/or Milestones due next week}
        \begin{enumerate}
            \item (BOTH) Work on Lab report exercises. Up until this point, we have been focusing on the instructions.
            \item (BOTH) initiate actual vulnerabilities
            \item (BOTH) Think about order of exercises. Exercise 4 has been defined, but nothing has been written up. (Look at documentation)
            \item (BOTH) Finish Network Diagrams for all exercises
            \item 
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
\end{document}